The Impact of Alternation

### 2017-05-10 draft.tex
ok

  \State let $u = a_1\ldots a_k$ be the label of the path from
  $\rootNode$ to $n$ in $\Art$

  \If{$\Accept{\A}(u)$ is satisfiable} \Comment{counterexample is
    real}

@@

With these considerations, Algorithm \ref{alg:predabs} uses a worklist
iteration to build an ART. We keep newly expanded nodes of $\Art$ in a
use a queue $\worklist$ to ensure a breadth-first exploration
strategy, which guarantees that the shortest counterexamples are
explored first. When the search encounters a counterexample $u$, it is
checked for spuriousness. If the counterexample is real, the procedure
returns a data word $w \in L(\A)$, which interleaves the input events
of $u$ with the data valuations from the model of $\Accept{\A}(u)$
(since $u$ is feasible, clearly $\Accept{\A}(u)$ is
satisfiable). Otherwise, if $u$ is spurious, we compute its pivot $p$
(line \ref{ln:pivot}), add the interpolants for the least unfeasible
suffix of $u$ to the set of predicates $\preds$, remove and recompute
the subtree of $\Art$ rooted at $p$.

@@

  \If{$n$ is not covered}
  \label{ln:not-covered}

  \If{$R(n) \cap F \neq \emptyset$} 
  \Comment{counterexample candidate}

  \If{$\mu(n)$ is satisfiable} 
  \Comment{counterexample is real}

@@

@@

  \State let $\rootNode,n_1,\ldots,n_k,n_{k+1}=n$ be the sequence of nodes from $\rootNode$ to $n$

@@

  \State $\Lambda(n_i) \leftarrow \Lambda(n_i) \wedge I_i$
  \Comment{strenghten the label of $n_i$}

  \State $\Call{Close}{n_i}$

@@

\State $\lhd \leftarrow \left(\lhd \setminus \set{ (p,q) \in \lhd \mid
  \text{$q$ is a successor of $x$}}\right) \cup \set{(x,y)}$

@@

The execution of Algorithm \ref{alg:impact} consists of three
phases\footnote{These phases correspond to the \textsc{Close},
  \textsc{Refine} and \textsc{Expand} procedures from the original
  description of \impact~\cite{mcmillan06}.}: \emph{close},
\emph{refine} and \emph{expand}. When a node $n$ is removed from the
worklist, it is first closed (line \ref{ln:close-worklist}) by finding
a lexicographically bigger node $m$ such that $\Lambda(n) \models
\Lambda(m)$, if one exists, and adding $(n,m)$ to $\lhd$. As in
Algorithm \ref{alg:predabs}, the intuition is that all successors of
$n$ are covered by the successors of $m$, thus for any feasible
counterexample that can be discovered from $n$ there exists a feasible
counterexample stemming in $m$, and we do not need to process $n$
further. If $n$ has not been covered in the close phase, we check if
it is the endpoint of a counterexample candidate, which can only be
the case

>>>>

  \State let $u = a_1\ldots a_k$ be the label of the path from
  $\rootNode$ to $n$

  \If{$\Accept{\A}(u)$ is satisfiable} \Comment{counterexample is
    feasible}

@@

With these considerations, Algorithm \ref{alg:predabs} uses a worklist
iteration to build an ART. We keep newly expanded nodes of $\Art$ in a
use a queue $\worklist$ to ensure a breadth-first exploration
strategy, which guarantees that the shortest counterexamples are
explored first. When the search encounters a counterexample $u$, it is
checked for spuriousness. If the counterexample is feasible, the procedure
returns a data word $w \in L(\A)$, which interleaves the input events
of $u$ with the data valuations from the model of $\Accept{\A}(u)$
(since $u$ is feasible, clearly $\Accept{\A}(u)$ is
satisfiable). Otherwise, if $u$ is spurious, we compute its pivot $p$
(line \ref{ln:pivot}), add the interpolants for the least unfeasible
suffix of $u$ to the set of predicates $\preds$, remove and recompute
the subtree of $\Art$ rooted at $p$.

@@

  \If{$n$ is not covered}

  \If{$R(n) \cap F \neq \emptyset$} 
  \label{ln:impact-cex}
  \Comment{counterexample candidate}

  \If{$\mu(n)$ is satisfiable} 
  \Comment{counterexample is feasible}

@@

  \State let $a_1 \ldots a_k$ be the label of the path from
  $\rootNode$ to $n$

@@

  \State let $\rootNode,n_1,\ldots,n_k,n_{k+1}=n$ be the sequence of nodes from $\rootNode$ to $n$
  \label{ln:refine-begin}

@@

  \State $\Lambda(n_i) \leftarrow \Lambda(n_i) \wedge I_i$
  \Comment{strenghten the label of $n_i$}
  \label{ln:close-refine}

  \State $\Call{Close}{n_i}$
  \label{ln:refine-end}

@@

\State $\lhd \leftarrow \left(\lhd \setminus \set{ (p,q) \in \lhd \mid
  \text{$q$ is a successor of $x$}}\right) \cup \set{(x,y)}$
\label{ln:close-uncover}

@@

The execution of Algorithm \ref{alg:impact} consists of three
phases\footnote{These phases correspond to the \textsc{Close},
  \textsc{Refine} and \textsc{Expand} procedures from the original
  description of \impact~\cite{mcmillan06}.}: \emph{close},
\emph{refine} and \emph{expand}. When a node $n$ is removed from the
worklist, it is first closed (line \ref{ln:close-worklist}) by finding
a lexicographically bigger node $m$ such that $\Lambda(n) \models
\Lambda(m)$, if one exists, and adding $(n,m)$ to $\lhd$. As in
Algorithm \ref{alg:predabs}, the intuition is that all successors of
$n$ are covered by the successors of $m$, thus for any feasible
counterexample that can be discovered from $n$ there exists a feasible
counterexample stemming in $m$, and we do not need to process $n$
further.

If $n$ has not been covered in the close phase, we check if it is the
endpoint of a counterexample candidate, which can only be the case
when the replacement set $R(n)$ contains at least one final state
(line \ref{ln:cex}). Observe that, if $u$ is the label of the path
from $\rootNode$ to $n$, then $\Accept{\A}(u)$ is satisfiable only if
it contains a (positive occurrence of) a final state. The
counterexample is feasible if and only if $\mu(n)$ is satisfiable, in
which case a model of $\mu(n)$ is obtained and a word $w \in L(\A)$
returned. Otherwise, the counterexample is spurious and the procedure
enters the refinement phase (lines \ref{ln:refine-begin} -
\ref{ln:refine-end}). The interpolant for $\mu(n)$ is used to
strenghten the labels of all the ancestors of $n$, by conjoining the
formulae of the interpolant to the existing labels. In this process,
some node might become eligible for coverage, therefore we attempt to
close each ancestor of $n$ that is impacted by the refinement (line
\ref{ln:close-refine}). Observe that, in this case the call to
$\Call{Close}{}$ must uncover each node which is covered by a
successor of $n$ (line \ref{ln:close-uncover} in the $\Call{Close}{}$
procedure). This is required because, due to the over-approximation of
the sets of reachable configurations, the covering relation is not
transitive, as explained in \cite{mcmillan06}.

Finally, we expand $n$ (lines \ref{ln:expand-begin} -
\ref{ln:expand-end}) by creating a new node for each successor via an
input event $a \in \Sigma$ and inserting it into the worklist. The
label of the
